---
title: "notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)

#library("tidyverse")
#ibrary("devtools")
#library("glue")
#library("dplyr")
#library("stringr")
#library("ggplot2")
#library("knitr")
#library("ggrepel")
#library("patchwork")
#library("janitor")
```

## Intro. 

Using the mpg data set, we can get a start to fucking up daddy fung. Make sure u get all the releveant libraries coz ur gonna need to be using them. 


## ytb

to load up the data, just write the name of the data set in the console, it'll give a fat tibble table. if u dunno anything, just put a ? mark inf front and you get a definition. 
```{r}
mpg
```

```{r carData}
library(tidyverse)
library(ggplot2)

carData <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class, shape = class)) +
  geom_smooth(data = filter(mpg, class == "subcompact"), se = FALSE)

carData

```

This carData graph uses data mpg, which also has a mapping argument, this makes the data "Mapped" to certain properties. In this case, the x and y axis is displ and hwy, this is easily exchanged for other shit. geom point is the dots on the plot, which can be any shape / color depending on how you set it. You can either go LGBTQ+ or set it to a random variable. Up to you. Geom Smooth is the line given, which we can use the filter function to find and make a line of best fit for the shit that we want. In this case, we have to declare the data used and what category that we want. 

idk what the fuck se is lmao

## Facuet Failure. 

Facet is a way to seperate the data into different graphs so its not clunky as fuck. Facet_wrap is to set how many rows int he data. We can also put same x and y variables in the data to save space. 

```{r pressure, echo=FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)

```

```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

```

What does facet wrap do? fuck use this ?
but, it wraps your data into different sets. Making the shit look pretty. 

We'll keep it there for the first week, Lyndal. Fuck you. 

